\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}

\usepackage{subfigure}
\usepackage{xcolor}
\usepackage{hyperref}
\include{defs}

\usepackage{lipsum}
%\usepackage[spanish]{babel}

\usepackage{booktabs}
\usepackage{array}
\usepackage{tabularx,multirow}

%\setcounter{page}{0}

%%%%%%%%%%%%%%%
% Title Page
\title{}
\author{}
\date{}
%%%%%%%%%%%%%%%

\begin{document}
\maketitle

%\tableofcontents
\clearpage
\section*{Welcome!}
Welcome to the beautiful city of Braga! Join us for the upcoming LTTA (learning, teaching and training activities), where we are going to talk and learn about Artificial Intelligence, all within the scope of the FAIaS project. 

This LTTA will be quite informal, but it will serve as a networking point to meet people from very different places (such as Spain or Belgium), we will have some good food together and last but not least we will have lots of fun. 

FAIaS fosters the knowledge and skills around Artificial Intelligence and Machine Learning at European schools. We aim for an Erasmus+ KA201 innovation in schools project. If funded, the project would run from March 2021 to August 2023.

Its goals are: 
\begin{enumerate}
    \item To foster the knowledge and skills around Artificial Intelligence and Machine Learning in European schools.
    \item To achieve goal \#1 in a way that is as inclusive as possible, with special attention to gender, economically and socially disadvantaged students, among others. 
    \item To raise awareness of the technical, social and ethical implications of Artificial Intelligence and Machine Learning.
\end{enumerate}

Its expected outcomes are:
\begin{enumerate}
    \item High-quality, open learning materials and experiences for educators and learners on AI and ML.
    \item Easy-to-use web-based (open source) software tools to support learning of AI and ML.
    \item Organization of activities for educators and learners on AI and ML (and make our learning materials, experiences and tools known).
\end{enumerate}


\subsection*{About the LTTA}

During the short-term training activity (4 days) organized in Braga in May-June 2022, the 20 FAIAS ambassadors selected by the partners from the participating countries (10 from Belgium, 5 from Spain and 5 from Portugal) will meet the FAIAS consortium and not only will be fully trained on the FAIAS objectives and introduced to the FAIAS outputs, but, most of all, they will be officially designated and invested with their role within the FAIAS project.

To be FAIAS Ambassador means to be ready, eager and willing to collaborate, contribute, and be committed to the FAIAS project implementation. FAIAS Ambassador will be a core figure within the project and the role will consist of and will require to:
\begin{itemize}
    \item Contribute in the drafting and revision of the main project outputs (collecting also contributions and suggestions from the local teachers)
    \item Act as a liaison between the FAIAS partners and the FAIAS local teachers communities 
    \item Train and support the local school teachers and colleagues to actively take part to FAIAS activities
    \item Encourage teachers to collaborate, to share ideas and projects, to use the FAIAS repository and tools 
    \item Moderate the FAIAS local community 
    \item Support with the dissemination of the FAIAS results to the school communities
\end{itemize}

During the short-term training activity the FAIAS ambassadors will not only be “theoretically” trained on the FAIAS results but will also have the chance to practise with the “Repository of existing AI content and initiatives” (IO2) and the “Peer-to-peer online community” (IO6). Interactive and collaborative sessions will be organized in order to share experience and proposals between the FAIAS Ambassadors and foster a strong collaboration among them.
In order words, the added value of LTTA consists in the official launch of the FAIAS peer-to-peer online community, which will be animated by the trained FAIAS ambassadors, and in the official publication of the FAIAS repository, ready to be used, benefited and exploited by the wider FAIAS community

In the table~\ref{tab:program} you can find the LTTA program.

\begin{table}
    \renewcommand{\arraystretch}{1.4}
     \begin{center}
     %\rowcolors{2}{gray!15}{white}
      \begin{tabular}{m{6cm} m{8cm}} % 2 cols 
        \hline
        \rowcolor{gray!35}\centering\arraybackslash\textbf{Day} & \centering\arraybackslash\textbf{Activity} \\
        \hline%\hline
        
        %\rowcolor{white}\multirow[t]{-2}{*}{\textbf{Tuesday, May 31 2022}} & \textbf{16:00 Welcome}(and activity)
        \centering\textbf{Tuesday, May 31 2022} &  \textbf{16:00 Welcome} (and activity) \newline
        \textbf{17:30 Talks by participants} \newline
        - Machine Learning in Education by Pablo Dúo Terrón \newline
        - Overview of AI activities developed by la Scientothèque by Yann-Aël Le Borgne 
        \newline
        \textbf{19:00 End} \newline
        \textbf{20:00 Dinner}
        \\ %\hline
        %\cdashline{2-3}
        \rowcolor{gray!15}
        \centering\textbf{Wednesday, June 1 2022} & \textbf{09:30 Breakfast} \newline \textbf{10:00 Intro to AI} \newline \textbf{13:00 Lunch} \newline 
        \textbf{15:00 Talks by participants II} \newline
        - AI Generation by Maria Inmaculada Caruana\newline
        - Peter De Deyn \newline
        - Problem solving with Machine Learning and Scratch by Álvaro Molina
        \newline
        \textbf{16:15 LearningML} \newline
        \textbf{17:30 Guided visit through Braga} \newline
        \textbf{19:00 End} \newline
        \textbf{20:00 Banket}
        \\ 
        \centering\textbf{Thursday, June 2 2022} & \textbf{09:30 Breakfast} \newline \textbf{10:00 Example lessons} Machine Learning in Citizenship lessons by Liliana Carrillo 
        \newline \textbf{13:00 Lunch} \newline
        \textbf{15:00 Preparation:} Create your lesson
        \newline
        \textbf{17:00 Presentations} \newline
        \textbf{17:30 End} \newline
        \textbf{20:00 Dinner} \\
        \rowcolor{gray!15}
        \centering\textbf{Friday, June 3 2022} &
        \textbf{09:30 Breakfast} \newline 
        \textbf{10:00 Presentation time} \newline 
        \textbf{12:00 Reflection and discussion time} \newline 
        \textbf{13:00 Lunch and farewell} \\
        \bottomrule%\hline
    \end{tabular}
      \caption[LTTA program]{LTTA program.}
      \label{tab:program}
     \end{center}
    \end{table}

    \newpage

\input{participants}

\end{document}
